---
title: "永和區 PM 2.5"
author: "Jerry Hsieh"
date: "2015年3月29日"
output: html_document
---

#### Introduction and Data

PM 2.5 is hot topic recently, I'm wondering what it will be around my living area?

The data come from http://taqm.epa.gov.tw/taqm/tw/YearlyDataDownload.aspx

行政院環境保護署 

環保署＼空氣品質監測網＼資料查詢與服務＼空氣品質測站＼歷年監測資料下載

### Loading data

```{r echo=FALSE, message=FALSE}
air <- read.csv("103YH20150324.csv", stringsAsFactor=FALSE)
airPM <- subset(air, Test.Item == "PM2.5")
airPM$Date <- as.Date(airPM$Date)
airPM[4:27] <- lapply(airPM[4:27], as.numeric)
library(ggplot2)
```

### calculate average by date and plot

Graph shown PM 2.5 is high

```{r, echo=FALSE}
library(ggplot2)
airPM$avg <- rowMeans(airPM[4:27], na.rm=TRUE)
plot(airPM$Date, airPM$avg)
abline(h=15)
```

Only `r sum(airPM$avg < 15)` days are under standard = 15

### when is best air quality within a day

Graph shown in the morning 4,5,6 o'clock are the best air quality within a day

```{r, echo=FALSE}
col <- colMeans(airPM[4:27], na.rm=TRUE)
plot(col)
```



